Species motif participation provides unique information about species risk of extinction

### 2022-06-15 manuscript/response_PRSB_round2.tex

\setlength{\parskip}{0.8em}
\setlength{\parindent}{0em}
\bibpunct{(}{)}{,}{a}{}{,}
\clubpenalty = 10000
\widowpenalty = 10000

\begin{document}

\section*{Response to reviewer comments}

\begin{flushleft}
\textbf{Manuscript number: } \texttt{RSPB-2021-2331} \\
``Species motif participation provides unique information about species risk of extinction''\\
Alyssa R. Cirtwill, Anna {\AA}kesson, Kate L. Wootton \& Anna Ekl\"of
\end{flushleft}

### 2022-06-16 manuscript/reorder_main_text.tex
Updates from Overleaf

\author{Alyssa R. Cirtwill$^{1*\dagger}$, Anna \r{A}kesson$^{2*}$, Kate L. Wootton$^{3}$, Anna Ekl\"{o}f$^{2}$} 
\date{
\small$^1$Spatial Foodweb Ecology Group\\
Research Centre for Ecological Change\\
Organismal and Evolutionary Biology Research Programm\\
Faculty of Biological and Environmental Sciences\\
University of Helsinki
\medskip
\small$^2$Department of Theoretical Biology, Chemistry, and Physics\\ 
Link\"{o}ping University\\
Link\"{o}ping, Sweden\\
\medskip
\small$^3$ BioFrontiers Institute\\
University of Colorado, Boulder\\
U.S.A.
\medskip
* Joint first authors
\medskip
$^\dagger$ Corresponding author\\
}

>>>>

\author{Alyssa R. Cirtwill$^{1*\dagger}$, Anna \r{A}kesson$^{2*}$, Kate L. Wootton$^{3}$, Anna Ekl\"{o}f$^{2}$} 
\date{
\small$^1$Spatial Foodweb Ecology Group\\
Research Centre for Ecological Change\\
Organismal and Evolutionary Biology Research Programm\\
Faculty of Biological and Environmental Sciences\\
University of Helsinki, Helsinki, Finland\\
\medskip
\small$^2$Department of Theoretical Biology, Chemistry, and Physics\\ 
Link\"{o}ping University, Link\"{o}ping, Sweden\\
\medskip
\small$^3$ BioFrontiers Institute\\
University of Colorado, Boulder, Boulder, U.S.A.\\
\medskip
* Joint first authors\\
\medskip
$^\dagger$ Corresponding author\\
}
